On hyperparameter tuning through Lipschitz global optimization

### 2023-09-30 2023/ITMO paper/elsarticle-template-num.tex
add table and fig. for time

@@

@@

\begin{figure}
\centering
\includegraphics[width=0.85\textwidth]{Fig8}
\caption{Time for tuning hyperparameters of the SVC algorithm to obtain good values of quality metrics on the Wilt dataset} \label{fig8}
\end{figure}

>>>>

\usepackage{graphicx}
\usepackage[table,xcdraw]{xcolor}
\usepackage{amssymb}

@@

% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{table}[]
\centering
\caption{Values of optimized metrics for the algorithm's averaged over 10 runs}
\label{tab:res}
\resizebox{\textwidth}{!}{%
\begin{tabular}{ccccccc}
\hline
\textbf{Dataset}                & \textbf{iOpt}                         & \textbf{Optuna(random)}                        & \textbf{Optuna(tpe)}                           & \textbf{Optuna(cmaes)}                         & \textbf{Optuna(nsgaii)}                        & \textbf{Hyperopt(tpe)}                         \\ \hline
                                & \multicolumn{6}{c}{\textbf{SVM}}                                                                                                                                                                                                                                                           \\ \hline
\textbf{Balance}                & {\color[HTML]{FE0000} 0.856}          & 0.856 $\pm$ 0.07\%                                 & 0.856 $\pm$ 0.23\%                                 & 0.834 $\pm$ 8.81\%                                 & \textbf{0.857 $\pm$ 0.31\%}                        & 0.856 $\pm$ 0.07\%                                 \\
\textbf{Bank-marketing}         & {\color[HTML]{FE0000} 0.894}          & 0.880 $\pm$ 1.65\%                                 & 0.892 $\pm$ 2.11\%                                 & 0.861 $\pm$ 5.16\%                                 & 0.879 $\pm$ 3.45\%                                 & \textbf{0.896 $\pm$ 0.48\%}                        \\
\textbf{Banknote}               & {\color[HTML]{FE0000} \textbf{0.992}} & 0.990 $\pm$ 0.04\%                                 & 0.991 $\pm$ 0.07\%                                 & 0.990 $\pm$ 0.20\%                                 & 0.990 $\pm$ 0.02\%                                 & 0.990 $\pm$ 0.00\%                                 \\
\textbf{Breast Cancer}          & {\color[HTML]{FE0000} 0.971}          & 0.970 $\pm$ 0.13\%                                 & 0.972 $\pm$ 0.19\%                                 & \textbf{0.973 $\pm$ 0.25\%}                        & 0.972 $\pm$ 0.13\%                                 & \textbf{0.973 $\pm$ 0.26\%}                        \\
\textbf{CarEvaluation}          & 0.349                                 & 0.350 $\pm$ 4.83\%                                 & {\color[HTML]{FE0000} \textbf{0.376 $\pm$ 4.57\%}} & 0.349 $\pm$ 4.83\%                                 & 0.355 $\pm$ 3.77\%                                 & 0.366 $\pm$ 3.21\%                                 \\
\textbf{CNAE-9}                 & {\color[HTML]{FE0000} \textbf{0.941}} & 0.938 $\pm$ 0.07\%                                 & 0.939 $\pm$ 0.05\%                                 & 0.939 $\pm$ 0.00\%                                 & 0.938 $\pm$ 0.05\%                                 & 0.939 $\pm$ 0.07\%                                 \\
\textbf{Credit   Approval}      & 0.878                                 & 0.881 $\pm$ 0.22\%                                 & {\color[HTML]{FE0000} \textbf{0.884 $\pm$ 0.18\%}} & 0.880 $\pm$ 0.23\%                                 & 0.880 $\pm$ 0.22\%                                 & 0.881 $\pm$ 0.21\%                                 \\
\textbf{Digits}                 & 0.984                                 & 0.984 $\pm$ 0.06\%                                 & {\color[HTML]{FE0000} \textbf{0.985 $\pm$ 0.02\%}} & \textbf{0.985 $\pm$ 0.05\%}                        & 0.984 $\pm$ 0.06\%                                 & \textbf{0.985 $\pm$ 0.03\%}                        \\
\textbf{Ecoli}                  & {\color[HTML]{FE0000} \textbf{0.863}} & 0.855 $\pm$ 0.28\%                                 & 0.861 $\pm$ 0.45\%                                 & 0.860 $\pm$ 0.59\%                                 & 0.855 $\pm$ 0.15\%                                 & 0.859 $\pm$ 0.28\%                                 \\
\textbf{Parkinsons}             & {\color[HTML]{FE0000} \textbf{0.931}} & 0.929 $\pm$ 0.33\%                                 & 0.930 $\pm$ 0.28\%                                 & 0.930 $\pm$ 0.19\%                                 & \textbf{0.931 $\pm$ 0.39\%}                        & \textbf{0.931 $\pm$ 0.36\%}                        \\
\textbf{Semeion}                & {\color[HTML]{FE0000} \textbf{0.942}} & 0.941 $\pm$ 0.10\%                                 & 0.941 $\pm$ 0.19\%                                 & \textbf{0.942 $\pm$ 0.12\%}                        & 0.941 $\pm$ 0.10\%                                 & \textbf{0.942 $\pm$ 0.09\%}                        \\
\textbf{Statlog   Segmentation} & {\color[HTML]{FE0000} \textbf{0.958}} & 0.955 $\pm$ 0.13\%                                 & 0.957 $\pm$ 0.07\%                                 & 0.956 $\pm$ 0.08\%                                 & 0.956 $\pm$ 0.06\%                                 & 0.956 $\pm$ 0.06\%                                 \\
\textbf{Wilt}                   & {\color[HTML]{FE0000} \textbf{0.704}} & 0.681 $\pm$ 1.90\%                                 & 0.699 $\pm$ 1.95\%                                 & 0.659 $\pm$ 17.91\%                                & 0.674 $\pm$ 1.89\%                                 & 0.696 $\pm$ 1.07\%                                 \\
\textbf{Zoo}                    & {\color[HTML]{FE0000} \textbf{0.979}} & {\color[HTML]{FE0000} \textbf{0.979 $\pm$ 0.00\%}} & {\color[HTML]{FE0000} \textbf{0.979 $\pm$ 0.00\%}} & {\color[HTML]{FE0000} \textbf{0.979 $\pm$ 0.00\%}} & {\color[HTML]{FE0000} \textbf{0.979 $\pm$ 0.00\%}} & {\color[HTML]{FE0000} \textbf{0.979 $\pm$ 0.00\%}} \\ \hline
\textbf{}                       & \multicolumn{6}{c}{\textbf{XGBoost}}                                                                                                                                                                                                                                                       \\ \hline
\textbf{Balance}                & 0.633                                 & 0.638 $\pm$ 1.16\%                                 & 0.650 $\pm$ 3.26\%                                 & 0.650 $\pm$ 1.73\%                                 & 0.645 $\pm$ 1.50\%                                 & {\color[HTML]{FE0000} \textbf{0.661 $\pm$ 2.63\%}} \\
\textbf{Bank-marketing}         & 0.918                                 & 0.918 $\pm$ 0.04\%                                 & {\color[HTML]{FE0000} \textbf{0.919 $\pm$ 0.04\%}} & 0.918 $\pm$ 0.04\%                                 & 0.918 $\pm$ 0.03\%                                 & 0.918 $\pm$ 0.03\%                                 \\
\textbf{Banknote}               & 0.994                                 & 0.994 $\pm$ 0.07\%                                 & \textbf{0.996 $\pm$ 0.07\%}                        & {\color[HTML]{FE0000} \textbf{0.996 $\pm$ 0.08\%}} & 0.995 $\pm$ 0.08\%                                 & 0.995 $\pm$ 0.09\%                                 \\
\textbf{Breast Cancer}          & 0.961                                 & 0.957 $\pm$ 0.27\%                                 & {\color[HTML]{FE0000} \textbf{0.963 $\pm$ 0.16\%}} & 0.961 $\pm$ 0.17\%                                 & 0.960 $\pm$ 0.39\%                                 & 0.960 $\pm$ 0.25\%                                 \\
\textbf{CarEvaluation}          & {\color[HTML]{FE0000} 0.980}          & 0.965 $\pm$ 0.88\%                                 & \textbf{0.983 $\pm$ 0.39\%}                        & 0.980 $\pm$ 0.28\%                                 & 0.974 $\pm$ 0.48\%                                 & 0.977 $\pm$ 0.38\%                                 \\
\textbf{CNAE-9}                 & 0.932                                 & 0.924 $\pm$ 0.83\%                                 & {\color[HTML]{FE0000} \textbf{0.937 $\pm$ 0.34\%}} & 0.935 $\pm$ 0.26\%                                 & 0.930 $\pm$ 0.53\%                                 & 0.935 $\pm$ 0.29\%                                 \\
\textbf{Credit   Approval}      & {\color[HTML]{FE0000} \textbf{0.901}} & 0.897 $\pm$ 0.29\%                                 & \textbf{0.901 $\pm$ 0.30\%}                        & 0.898 $\pm$ 0.22\%                                 & 0.899 $\pm$ 0.32\%                                 & 0.898 $\pm$ 0.28\%                                 \\
\textbf{Digits}                 & 0.975                                 & 0.973 $\pm$ 0.17\%                                 & 0.976 $\pm$ 0.15\%                                 & {\color[HTML]{FE0000} \textbf{0.978 $\pm$ 0.15\%}} & 0.975 $\pm$ 0.15\%                                 & 0.976 $\pm$ 0.15\%                                 \\
\textbf{Ecoli}                  & {\color[HTML]{FE0000} \textbf{0.865}} & 0.852 $\pm$ 0.55\%                                 & \textbf{0.865 $\pm$ 0.53\%}                        & 0.864 $\pm$ 0.24\%                                 & 0.856 $\pm$ 0.40\%                                 & 0.861 $\pm$ 0.37\%                                 \\
\textbf{Parkinsons}             & {\color[HTML]{FE0000} 0.950}          & 0.944 $\pm$ 0.24\%                                 & \textbf{0.953 $\pm$ 0.42\%}                        & 0.952 $\pm$ 0.16\%                                 & 0.949 $\pm$ 0.32\%                                 & \textbf{0.953 $\pm$ 0.42\%}                        \\
\textbf{Semeion}                & 0.940                                 & 0.939 $\pm$ 0.48\%                                 & {\color[HTML]{FE0000} \textbf{0.951 $\pm$ 0.20\%}} & 0.950 $\pm$ 0.14\%                                 & 0.942 $\pm$ 0.39\%                                 & 0.948 $\pm$ 0.25\%                                 \\
\textbf{Statlog   Segmentation} & 0.982                                 & 0.981 $\pm$ 0.11\%                                 & \textbf{0.984 $\pm$ 0.24\%}                        & 0.984 $\pm$ 0.07\%                                 & 0.983 $\pm$ 0.13\%                                 & {\color[HTML]{FE0000} \textbf{0.984 $\pm$ 0.08\%}} \\
\textbf{Wilt}                   & 0.868                                 & 0.842 $\pm$ 1.41\%                                 & {\color[HTML]{FE0000} \textbf{0.872 $\pm$ 0.32\%}} & 0.867 $\pm$ 0.43\%                                 & 0.858 $\pm$ 0.88\%                                 & 0.865 $\pm$ 0.34\%                                 \\
\textbf{Zoo}                    & {\color[HTML]{FE0000} \textbf{1.000}} & 0.992 $\pm$ 0.86\%                                 & 0.992 $\pm$ 0.79\%                                 & 0.989 $\pm$ 0.73\%                                 & 0.998 $\pm$ 0.47\%                                 & 0.987 $\pm$ 0.64\%                                 \\ \hline
\textbf{}                       & \multicolumn{6}{c}{\textbf{MLP}}                                                                                                                                                                                                                                                           \\ \hline
\textbf{Balance}                & 0.968                                 & 0.967 $\pm$ 0.41\%                                 & {\color[HTML]{FE0000} \textbf{0.973 $\pm$ 0.30\%}} & 0.966 $\pm$ 0.39\%                                 & 0.969 $\pm$ 0.32\%                                 & 0.970 $\pm$ 0.32\%                                 \\
\textbf{Bank-marketing}         & 0.914                                 & 0.914 $\pm$ 0.05\%                                 & \textbf{0.915 $\pm$ 0.04\%}                        & 0.914 $\pm$ 0.03\%                                 & {\color[HTML]{FE0000} \textbf{0.915 $\pm$ 0.03\%}} & {\color[HTML]{FE0000} \textbf{0.915 $\pm$ 0.03\%}} \\
\textbf{Banknote}               & {\color[HTML]{FE0000} \textbf{1.000}} & {\color[HTML]{FE0000} \textbf{1.000 $\pm$ 0.00\%}} & {\color[HTML]{FE0000} \textbf{1.000 $\pm$ 0.00\%}} & {\color[HTML]{FE0000} \textbf{1.000 $\pm$ 0.00\%}} & {\color[HTML]{FE0000} \textbf{1.000 $\pm$ 0.00\%}} & {\color[HTML]{FE0000} \textbf{1.000 $\pm$ 0.00\%}} \\
\textbf{Breast Cancer}          & {\color[HTML]{FE0000} \textbf{0.974}} & \textbf{0.974 $\pm$ 0.16\%}                        & \textbf{0.974 $\pm$ 0.07\%}                        & 0.973 $\pm$ 0.12\%                                 & \textbf{0.974 $\pm$ 0.09\%}                        & \textbf{0.974 $\pm$ 0.11\%}                        \\
\textbf{CarEvaluation}          & 0.996                                 & 0.999 $\pm$ 0.10\%                                 & 0.993 $\pm$ 1.33\%                                 & 0.982 $\pm$ 1.98\%                                 & \textbf{1.000 $\pm$ 0.03\%}                        & {\color[HTML]{FE0000} \textbf{1.000 $\pm$ 0.00\%}} \\
\textbf{CNAE-9}                 & 0.957                                 & 0.955 $\pm$ 0.12\%                                 & 0.958 $\pm$ 0.06\%                                 & 0.955 $\pm$ 0.14\%                                 & 0.957 $\pm$ 0.15\%                                 & {\color[HTML]{FE0000} \textbf{0.959 $\pm$ 0.17\%}} \\
\textbf{Credit   Approval}      & 0.885                                 & 0.885 $\pm$ 0.19\%                                 & {\color[HTML]{FE0000} \textbf{0.889 $\pm$ 0.15\%}} & 0.885 $\pm$ 0.17\%                                 & 0.886 $\pm$ 0.20\%                                 & 0.888 $\pm$ 0.13\%                                 \\
\textbf{Digits}                 & {\color[HTML]{FE0000} \textbf{0.984}} & 0.983 $\pm$ 0.14\%                                 & \textbf{0.984 $\pm$ 0.06\%}                        & 0.982 $\pm$ 0.06\%                                 & 0.983 $\pm$ 0.09\%                                 & \textbf{0.984 $\pm$ 0.07\%}                        \\
\textbf{Ecoli}                  & 0.848                                 & 0.857 $\pm$ 0.42\%                                 & \textbf{0.861 $\pm$ 0.53\%}                        & 0.859 $\pm$ 0.40\%                                 & 0.857 $\pm$ 0.53\%                                 & {\color[HTML]{FE0000} \textbf{0.861 $\pm$ 0.41\%}} \\
\textbf{Parkinsons}             & {\color[HTML]{FE0000} 0.963}          & 0.961 $\pm$ 0.28\%                                 & 0.965 $\pm$ 0.27\%                                 & 0.959 $\pm$ 0.32\%                                 & 0.962 $\pm$ 0.20\%                                 & \textbf{0.964 $\pm$ 0.30\%}                        \\
\textbf{Semeion}                & {\color[HTML]{FE0000} 0.945}          & 0.941 $\pm$ 0.14\%                                 & \textbf{0.946 $\pm$ 0.23\%}                        & 0.940 $\pm$ 0.11\%                                 & 0.943 $\pm$ 0.28\%                                 & 0.945 $\pm$ 0.15\%                                 \\
\textbf{Statlog   Segmentation} & 0.976                                 & 0.977 $\pm$ 0.12\%                                 & \textbf{0.979 $\pm$ 0.17\%}                        & 0.976 $\pm$ 0.18\%                                 & 0.978 $\pm$ 0.04\%                                 & {\color[HTML]{FE0000} \textbf{0.979 $\pm$ 0.04\%}} \\
\textbf{Wilt}                   & {\color[HTML]{FE0000} 0.906}          & 0.904 $\pm$ 0.15\%                                 & \textbf{0.907 $\pm$ 0.26\%}                        & 0.906 $\pm$ 0.23\%                                 & 0.906 $\pm$ 0.03\%                                 & \textbf{0.907 $\pm$ 0.14\%}                        \\
\textbf{Zoo}                    & {\color[HTML]{FE0000} \textbf{1.000}} & 0.988 $\pm$ 0.97\%                                 & 0.990 $\pm$ 0.90\%                                 & 0.995 $\pm$ 0.80\%                                 & 0.996 $\pm$ 0.86\%                                 & 0.995 $\pm$ 0.81\%                                 \\ \hline
\end{tabular}%
}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{fig_time}
\caption{Time for tuning hyperparameters of the SVC algorithm to obtain good values of quality metrics on the Wilt dataset} \label{fig8}
\end{figure}
